### 2018-07-22 express2018/formal.tex
Reworked HOL4 introduction

\section{Formalisation}
\label{s:for}
We highlight here a formalisation of CCS
in the HOL theorem
prover (HOL4) \cite{slind2008brief},
including the new concepts and theorems proposed in the first half of
this paper.
%  The main purpose is to convince the readers that, there's no flaw
%  in the informal proofs. 
The whole formalisation can be found 
in \cite{Tian:2017wrba}  or in 
 in the official example folder of HOL4 source
code\footnote{\url{https://github.com/HOL-Theorem-Prover/HOL}}. The
work consists of about 20,000 lines of proof scripts in Standard ML;
it develops
some pioneering work by Nesi \cite{Nesi:1992ve}, in
1992-1995.

Higher Order Logic (or ``HOL Logic'') \cite{hollogic} stands for simple-typed $\lambda$-calculus plus Hilbert
choice operator, axiom of infinity, and rank-1 polymorphism (type
variables). HOL4 implemented the original HOL Logic, 
while some other theorem provers in HOL family (e.g. Isabelle/HOL) have
certain extensions.
%  (they made the formal language more powerful,
% but they also bring the possibilities that the entire logic becomes
% inconsistent). 
Indeed the HOL Logic has considerable simpler logic
foundations than most other theorem provers. %, e.g. Coq. 
As a result,
formal theories in HOL can be easily migrated (sometimes even
automatically) into other theorem provers.

HOL4 is written in Standard ML (ML for abbreviation), which plays three roles here:
\begin{enumerate}
\item It serves as the underlying implementation language for the core HOL engine;
\item it is used to implement tactics (and tacticals) for writing proofs;
\item it is used as the command language of the HOL interactive shell.
\end{enumerate}
Further, in the same language
 HOL4 users can write complex automatic
verification tools  by calling HOL's interactive theorem proving facilities.

@@

In this
formalisation we consider only single equations/contractions. 
This  %considerably
 simplifies the required proof steps in HOL   while enhancing the
 reading of the scripts.
%   still aligned with
% their informal proofs.
%  (on 
% the extension  to multiple equations/contractions
% see also  Section~\ref{s:concl}).

>>>>

\section{Formalisation}
\label{s:for}
We highlight here a formalisation of CCS
in the HOL theorem
prover (HOL4) \cite{slind2008brief},
including the new concepts and theorems proposed in the first half of
this paper.
%  The main purpose is to convince the readers that, there's no flaw
%  in the informal proofs. 
The whole formalisation (apart from minor fixes and extensions in this
paper)
is described in \cite{Tian:2017wrba}, and the
proof scripts are in HOL4 official examples\footnote{\url{https://github.com/HOL-Theorem-Prover/HOL/tree/master/examples/CCS}}. The
work consists of about 20,000 lines of proof scripts in Standard ML.

Higher Order Logic (or \emph{HOL Logic}) \cite{hollogic} is a variant of
Church’s simple theory of types (STT) \cite{church1940formulation}
\hl{(or \emph{simple-typed $\lambda$-calculus}),
plus a higher order version of Hilbert's choice operator $\varepsilon$,
Axiom of Infinity, and Rank-1 (prenex) polymorphism.}
HOL4 has implemented the original HOL Logic, 
while some other theorem provers in HOL family (e.g. Isabelle/HOL) have
certain extensions.
%  (they made the formal language more powerful,
% but they also bring the possibilities that the entire logic becomes
% inconsistent). 
Indeed the HOL Logic has considerable simpler logical
foundations than most other theorem provers. %, e.g. Coq. 
As a result,
formal theories built in HOL4 is relatively easier convincible and can
be also easily migrated into other theorem provers,
sometimes even automatically \cite{hurd2011opentheory}.

HOL4 is written in Standard ML, a single programming language who
plays three different roles: (The situation is quite different in
other systems like Coq\footnote{\hl{The Coq Proof Assistant.} \url{https://coq.inria.fr}}.)
\begin{enumerate}
\item It serves as the underlying implementation language for the core HOL engine;
\item it is used to implement tactics (and tacticals) for writing proofs;
\item it is used as the command language of the HOL interactive shell.
\end{enumerate}
\hl{Moreover, using} the same language HOL4 users can write complex automatic
verification tools by calling HOL's interactive theorem proving facilities.

@@

\textbf{In this
formalisation we consider only single-variable equations/contractions.}
This considerably
 simplifies the required proofs in HOL, enhances the readibility of
 proof scripts, \hl{without loss of generality (for paper proofs, the
 general case is just a routine
 adaptation).}
%   still aligned with
% their informal proofs.
%  (on 
% the extension  to multiple equations/contractions
% see also  Section~\ref{s:concl}).
